\cvsection{Experience}

\begin{cventries}
  \cventry
    {Data scientist}
    {Freepoint Commodities}
    {Zug, Switzerland}
    {Sep. 2024 - Present}
    {
    \begin{itemize}
        \item \textbf{Country-level power forecasting}: forecasted country level wind and solar energy production, focusing on coverage calibration and probabilistic methods. Improved upon external vendor forecasts for the 7–15 day horizon, reducing MAE by 8\%.
        \item \textbf{Data infrastructure}: led a cross-functional team (meteorologists + IT) to design and deliver a scalable weather datalake (zarr/parquet-based), streamlining data accessibility for analytics.
        \item \textbf{Software standardization}: developed and maintained core Python libraries adopted by cross-functional teams, standardizing data access and reducing onboarding times for new analysts.
        \item \textbf{Strategic cost savings}: built a performance dashboard enabling traders to benchmark vendor accuracy across various lead times and metrics. This led to the cancellation of sub-optimal subscriptions, saving the company $\sim$€200k/y.
    \end{itemize}
    }




\begin{cventries}
  \cventry
    {Data scientist}
    {DXT Commodities SA}
    {Lugano, Switzerland}
    {Mar. 2019 - Jul. 2024}
    {
    \begin{itemize}
        \item \textbf{Multi-asset forecasting}: forecasted 4Gw renewable portfolio power generation (wind, solar, hydro, consumption), power and gas demand of EU countries.
        \item \textbf{Anomaly detection}: developed an automatic outage and outlier detection for dispatched power plants.
        \item \textbf{Algorithmic trading}: designed and implemented an intraday trading strategy for the Italian power market (up to 6 hours before delivery), achieving a Sharpe ratio of 2.1.
        \item \textbf{MLOps architecture}: Built the end-to-end MLOps infrastructure from the ground up, integrating Cookiecutter, MLflow, Jenkins, and Prefect to automate the model lifecycle.
    \end{itemize}
    }
    
    
  \cventry
    {Quantitative Risk Analyst in Group Financial Risk Methodologies}
    {UniCredit S.p.a}
    {Milan, Italy}
    {Apr. 2017 - Feb. 2019}
    {
    %%\begin{itemize}
    %%    \item Analysis of sensitivity of fixed income portofolios.
    %%    \item Modelisation and implementation of regulatory risk measures (Expected Shortfall).
    %%\end{itemize} 
    }
    
\iffalse
  \cventry
    {Stage in Group Financial Risk Methodologies}
    {UniCredit S.p.a}
    {Milan, Italy}
    {May 2017 - Nov. 2017}
    {}
 \fi
\end{cventries}
